Scalable Clustering of Genotype Information using MapReduce

### 2014-05-14 doc/publications/incob2014/paper.tex
added image

\section*{Figures}
  \begin{figure}[h!]
  \caption{\csentence{Sample figure title.}
      A short description of the figure content
      should go here.}
      \end{figure}

>>>>

\section*{Figures}
  \begin{figure}[h!]
  \caption{\csentence{Illustration of Mahout-based clustering of genotypes.}
      The image shows how the here introduced interface converts the vcf file to a mahout usable vector-based data type. Based on k-means it illustrates how the Map-step procedure groups of vectors by their nearest cluster center and the Reduce-step averages the vectors in each group to find the new value of the updated cluster center. The mahout-produced output is then converted into a visualisation.}
      \end{figure}
